---
title: "Package yokoe Documentation"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, warning = TRUE, message = TRUE)
```

## Function: `area`

**Documentation:**

```
Return a area from polygon xy coordinates

Description:

     Return a area from polygon xy coordinates

Usage:

     area(xy)
     
Arguments:

      xy: a atrix or data frame of xy coordinates

Value:

     a vector of polygon area

Examples:

     xy<-data.frame(x=c(0,1,2,1),y=c(1,2,1,0))
     plot(xy,type="b") ; polygon(xy)
     area(xy)
     
```

**Examples (from .Rd):**
```r
### Name: area
### Title: Return a area from polygon xy coordinates
### Aliases: area

### ** Examples

xy<-data.frame(x=c(0,1,2,1),y=c(1,2,1,0))
plot(xy,type="b") ; polygon(xy)
area(xy)






```

**Executed Example:**
```{r area_example, eval=TRUE, error=TRUE}
try(example('area', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `circumference`

**Documentation:**

```
Return circumference length of polygon line

Description:

     Return circumference length of polygon line

Usage:

     circumference(l.)
     
Arguments:

      l.: data frame of line coordinates (x,y)

Value:

     a numeric of circumference length of polygon line

Examples:

     l. <- data.frame(x=c(0,0,1,1),y=c(0,1,1,0))
     plot(l.,type="b") ; polygon(l.)
     circumference(l.)
     
```

**Examples (from .Rd):**
```r
### Name: circumference
### Title: Return circumference length of polygon line
### Aliases: circumference

### ** Examples

l. <- data.frame(x=c(0,0,1,1),y=c(0,1,1,0))
plot(l.,type="b") ; polygon(l.)
circumference(l.)



```

**Executed Example:**
```{r circumference_example, eval=TRUE, error=TRUE}
try(example('circumference', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `degree`

**Documentation:**

```
Constant for conversion from degree to radian ####

Description:

     Constant for conversion from degree to radian ####

Usage:

     degree
     
Format:

     An object of class 'numeric' of length 1.

```



**Executed Example:**
```{r degree_example, eval=TRUE, error=TRUE}
try(example('degree', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `dstpp`

**Documentation:**

```
Return vector for distance between adjacent two points

Description:

     Return vector for distance between adjacent two points

Usage:

     dstpp(x, y)
     
Arguments:

       x: vector of x coordinates

       y: vector of y coordinates

Value:

     vector for distance between adjacent two points

Examples:

     l.<-TR@L[[1]]
     plot(l.)
     x<-l.[,1] ;y<-l.[,2]
     dstpp(x,y)
     
```

**Examples (from .Rd):**
```r
### Name: dstpp
### Title: Return vector for distance between adjacent two points
### Aliases: dstpp

### ** Examples

l.<-TR@L[[1]]
plot(l.)
x<-l.[,1] ;y<-l.[,2]
dstpp(x,y)



```

**Executed Example:**
```{r dstpp_example, eval=TRUE, error=TRUE}
try(example('dstpp', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `f123`

**Documentation:**

```
2D graphics of hose floor 1-2-3

Description:

     2D graphics of hose floor 1-2-3

Usage:

     f123()
     
Examples:

     f123()
     
```

**Examples (from .Rd):**
```r
### Name: f123
### Title: 2D graphics of hose floor 1-2-3
### Aliases: f123

### ** Examples

f123()




```

**Executed Example:**
```{r f123_example, eval=TRUE, error=TRUE}
try(example('f123', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `g`

**Documentation:**

```
Title

Description:

     Title

Usage:

     g()
     
Examples:

     g()
     
```

**Examples (from .Rd):**
```r
### Name: g
### Title: Title
### Aliases: g

### ** Examples

g()




```

**Executed Example:**
```{r g_example, eval=TRUE, error=TRUE}
try(example('g', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `hashira2d`

**Documentation:**

```
Title

Description:

     Title

Usage:

     hashira2d(h. = hashira, label = F)
     
Arguments:

       d:

Examples:

     plot_gaiheki()
     hashira2d()
     
```

**Examples (from .Rd):**
```r
### Name: hashira2d
### Title: Title
### Aliases: hashira2d

### ** Examples

plot_gaiheki()
hashira2d()




```

**Executed Example:**
```{r hashira2d_example, eval=TRUE, error=TRUE}
try(example('hashira2d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `hashira3d`

**Documentation:**

```
Title

Description:

     Title

Usage:

     hashira3d(h. = hashira)
     
Arguments:

       d:

Examples:

     yokoe3d()
     hashira3d()
     
```

**Examples (from .Rd):**
```r
### Name: hashira3d
### Title: Title
### Aliases: hashira3d

### ** Examples

yokoe3d()
hashira3d()




```

**Executed Example:**
```{r hashira3d_example, eval=TRUE, error=TRUE}
try(example('hashira3d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `kabe2d`

**Documentation:**

```
Title

Description:

     Title

Usage:

     kabe2d(d = kabe.)
     
Arguments:

       d:

Examples:

     plot_gaiheki()
     hashira2d(label=T)
     #  to.<-read.csv("data_raw/to.csv")
     kabe.<- data.frame(no=1,id="to_rouka",space="engawa", floor=1,  x=3447.948,y=1643.072, z=700, w=4800, d=180,h=1800,deg=90)
     kabe2d(kabe.)
     
```

**Examples (from .Rd):**
```r
### Name: kabe2d
### Title: Title
### Aliases: kabe2d

### ** Examples

plot_gaiheki()
hashira2d(label=T)
#  to.<-read.csv("data_raw/to.csv")
kabe.<- data.frame(no=1,id="to_rouka",space="engawa", floor=1,  x=3447.948,y=1643.072, z=700, w=4800, d=180,h=1800,deg=90)
kabe2d(kabe.)






```

**Executed Example:**
```{r kabe2d_example, eval=TRUE, error=TRUE}
try(example('kabe2d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `kabe_line`

**Documentation:**

```
Title

Description:

     Title

Usage:

     kabe_line(. = kabe_F1)
     
Arguments:

       .:

Examples:

     f123()
     kabe_line(kabe_F1)
     
```

**Examples (from .Rd):**
```r
### Name: kabe_line
### Title: Title
### Aliases: kabe_line

### ** Examples

f123()
kabe_line(kabe_F1)




```

**Executed Example:**
```{r kabe_line_example, eval=TRUE, error=TRUE}
try(example('kabe_line', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `kaidan2d`

**Documentation:**

```
Title

Description:

     Title

Usage:

     kaidan2d(kd = kaidan)
     
Arguments:

    kd.z:

Examples:

     kaidan<-data.frame(w=1800,d=900,h=2700,sn=12,deg=0)
     kaidan<-data.frame(id="f12",x=3600,y=5850,z=700,kaidan)
     kaidan[2,1] <-c("f23");kaidan[2,2:9] <- c(9000,5850,2700,900,800,900,4,0)
     str(kaidan)
     f123()
     kaidan2d(kaidan)#  #save(kaidan,file="data/kaidan.RData")
     #save(kaidan,file="data/kaidan.RData")
     
```

**Examples (from .Rd):**
```r
### Name: kaidan2d
### Title: Title
### Aliases: kaidan2d

### ** Examples

kaidan<-data.frame(w=1800,d=900,h=2700,sn=12,deg=0)
kaidan<-data.frame(id="f12",x=3600,y=5850,z=700,kaidan)
kaidan[2,1] <-c("f23");kaidan[2,2:9] <- c(9000,5850,2700,900,800,900,4,0)
str(kaidan)
f123()
kaidan2d(kaidan)#  #save(kaidan,file="data/kaidan.RData")
#save(kaidan,file="data/kaidan.RData")




```

**Executed Example:**
```{r kaidan2d_example, eval=TRUE, error=TRUE}
try(example('kaidan2d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `nearest`

**Documentation:**

```
Title

Description:

     Title

Usage:

     nearest(x, X)
     
Arguments:

      xy: matrix of x,y coordinates

      XY: matrix of inclde x,y coordinates

Examples:

     X<-1:20
     x<-10:15+rnorm(6)
     nearest(x,X)
     
```

**Examples (from .Rd):**
```r
### Name: nearest
### Title: Title
### Aliases: nearest

### ** Examples




X<-1:20
x<-10:15+rnorm(6)
nearest(x,X)




```

**Executed Example:**
```{r nearest_example, eval=TRUE, error=TRUE}
try(example('nearest', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `package_docs_with_examples`

**Documentation:**

```
Generate Package Documentation with Examples and Knit to HTML

Description:

     Generate Package Documentation with Examples and Knit to HTML

Usage:

     package_docs_with_examples(
       package_name,
       output_rmd = "package_docs_with_examples.Rmd",
       output_html = "package_docs_with_examples.html"
     )
     
Arguments:

package_name: The name of the package (character string)

output_rmd: The output Rmd filename (default:
          "package_docs_with_examples.Rmd")

output_html: The output HTML filename (default:
          "package_docs_with_examples.html")

Value:

     None. The Rmd and HTML files are generated in the current working
     directory.

Examples:

     package_docs_with_examples("yokoe")
     
```

**Examples (from .Rd):**
```r
### Name: package_docs_with_examples
### Title: Generate Package Documentation with Examples and Knit to HTML
### Aliases: package_docs_with_examples

### ** Examples

package_docs_with_examples("yokoe")




```

**Executed Example:**
```{r package_docs_with_examples_example, eval=TRUE, error=TRUE}
try(example('package_docs_with_examples', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `plot_gaiheki`

**Documentation:**

```
Title

Description:

     Title

Usage:

     plot_gaiheki()
     
Examples:

     #data(package="yokoe")
     plot_gaiheki()
     
```

**Examples (from .Rd):**
```r
### Name: plot_gaiheki
### Title: Title
### Aliases: plot_gaiheki

### ** Examples

#data(package="yokoe")
plot_gaiheki()




```

**Executed Example:**
```{r plot_gaiheki_example, eval=TRUE, error=TRUE}
try(example('plot_gaiheki', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_append`

**Documentation:**

```
Title

Description:

     Title

Usage:

     points_append(xy = p2)
     
Arguments:

      xy:

Examples:

     f123()
     kabe2d()
     points(p2)
     p2_append <- points_append(p2)
     points(p2_append,pch=10)
     p2<-p2_append
     # save(p2,file="data/p2.RData")
     
```

**Examples (from .Rd):**
```r
### Name: points_append
### Title: Title
### Aliases: points_append

### ** Examples

f123()
kabe2d()
points(p2)
p2_append <- points_append(p2)
points(p2_append,pch=10)
p2<-p2_append
# save(p2,file="data/p2.RData")




```

**Executed Example:**
```{r points_append_example, eval=TRUE, error=TRUE}
try(example('points_append', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_delete`

**Documentation:**

```
Title

Description:

     Title

Usage:

     points_delete(d)
     
Arguments:

       y:

Examples:

     .<-data.frame(x=1:20 ,y=x^1.5)
     plot(.$x,.$y)
     .<-points_delete(.,type="o",col="red")
     plot(.$x,.$y)
     
```

**Examples (from .Rd):**
```r
### Name: points_delete
### Title: Title
### Aliases: points_delete

### ** Examples

.<-data.frame(x=1:20 ,y=x^1.5)
plot(.$x,.$y)
.<-points_delete(.,type="o",col="red")
plot(.$x,.$y)



```

**Executed Example:**
```{r points_delete_example, eval=TRUE, error=TRUE}
try(example('points_delete', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_grid_snap`

**Documentation:**

```
points_grid_snap

Description:

     points_grid_snap

Usage:

     points_grid_snap(xy = p., grid = 450)
     
Arguments:

    grid:

Examples:

     p.<-data.frame(x=runif(30) , y=runif(30))
     grid.=0.1
     plot(p.)
     abline(h=seq(0,1,grid.),v=seq(0,1,grid.))
     p..<-points_grid_snap(xy=p.,grid=grid.)
     points(p..,col="red")
     
```

**Examples (from .Rd):**
```r
### Name: points_grid_snap
### Title: points_grid_snap
### Aliases: points_grid_snap

### ** Examples

p.<-data.frame(x=runif(30) , y=runif(30))
grid.=0.1
plot(p.)
abline(h=seq(0,1,grid.),v=seq(0,1,grid.))
p..<-points_grid_snap(xy=p.,grid=grid.)
points(p..,col="red")



```

**Executed Example:**
```{r points_grid_snap_example, eval=TRUE, error=TRUE}
try(example('points_grid_snap', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_move`

**Documentation:**

```
Title

Description:

     Title

Usage:

     points_move(xy = p2)
     
Arguments:

      xy:

Examples:

     f123()
     points(p2)
     p2_corrected <- points_move(p2)
     points(p2_corrected,pch=10)
     p2<-p2_corrected
     # save(p2,file="data/p2.RData")
     
```

**Examples (from .Rd):**
```r
### Name: points_move
### Title: Title
### Aliases: points_move

### ** Examples

f123()
points(p2)
p2_corrected <- points_move(p2)
points(p2_corrected,pch=10)
p2<-p2_corrected
# save(p2,file="data/p2.RData")





```

**Executed Example:**
```{r points_move_example, eval=TRUE, error=TRUE}
try(example('points_move', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_nearest`

**Documentation:**

```
Title

Description:

     Title

Usage:

     points_nearest(xy, XY)
     
Arguments:

      xy: data frame of x,y coordinates

      XY: data frame of inclde x,y coordinates

Examples:

     XY<-data.frame(x=1:20 ,y=(1:20)^1)
     plot(XY)
     text(XY[,1],XY[,2]-1,1:20)
     xy<-cbind(x=10:15 ,y=(10:15)^1.01)
     points(xy,col="red")
      points_nearest(xy,XY)
     
```

**Examples (from .Rd):**
```r
### Name: points_nearest
### Title: Title
### Aliases: points_nearest

### ** Examples




XY<-data.frame(x=1:20 ,y=(1:20)^1)
plot(XY)
text(XY[,1],XY[,2]-1,1:20)
xy<-cbind(x=10:15 ,y=(10:15)^1.01)
points(xy,col="red")
 points_nearest(xy,XY)



```

**Executed Example:**
```{r points_nearest_example, eval=TRUE, error=TRUE}
try(example('points_nearest', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `points_rect_select`

**Documentation:**

```
Title

Description:

     Title

Usage:

     points_rect_select(x, y)
     
Arguments:

       y:

Examples:

     x<-1:20 ; y<- x^1.5
     plot(x,y)
     points_rect_select(x,y)
     
```

**Examples (from .Rd):**
```r
### Name: points_rect_select
### Title: Title
### Aliases: points_rect_select

### ** Examples

x<-1:20 ; y<- x^1.5
plot(x,y)
points_rect_select(x,y)



```

**Executed Example:**
```{r points_rect_select_example, eval=TRUE, error=TRUE}
try(example('points_rect_select', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `to2d`

**Documentation:**

```
Title

Description:

     Title

Usage:

     to2d(d = to)
     
Arguments:

       d:

Examples:

     plot_gaiheki()
     hashira2d()
     #  to.<-read.csv("data_raw/to.csv")
     to.<- data.frame(no=1,id="to_rouka",space="engawa", floor=1,  x=3447.948,y=1643.072, z=700, w=11800, d=100,h=1800,deg=0)
     to2d(to.)
     
```

**Examples (from .Rd):**
```r
### Name: to2d
### Title: Title
### Aliases: to2d

### ** Examples

plot_gaiheki()
hashira2d()
#  to.<-read.csv("data_raw/to.csv")
to.<- data.frame(no=1,id="to_rouka",space="engawa", floor=1,  x=3447.948,y=1643.072, z=700, w=11800, d=100,h=1800,deg=0)
to2d(to.)




```

**Executed Example:**
```{r to2d_example, eval=TRUE, error=TRUE}
try(example('to2d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `vh2xy`

**Documentation:**

```
Title

Description:

     Title

Usage:

     vh2xy(v, h)
     
Arguments:

       h:

Examples:

     f123()
     points(vh2xy(4,1))
     
```

**Examples (from .Rd):**
```r
### Name: vh2xy
### Title: Title
### Aliases: vh2xy

### ** Examples

f123()
points(vh2xy(4,1))



```

**Executed Example:**
```{r vh2xy_example, eval=TRUE, error=TRUE}
try(example('vh2xy', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

## Function: `yokoe3d`

**Documentation:**

```
3D plot of Yokoe house

Description:

     3D plot of Yokoe house

Usage:

     yokoe3d()
     
Examples:

     #library(rgl)
     yokoe3d()
     #lines3d(seq(-10000,80000,900),seq(-10000,180000,900),0,col="gray")
     f123()
     
```

**Examples (from .Rd):**
```r
### Name: yokoe3d
### Title: 3D plot of Yokoe house
### Aliases: yokoe3d

### ** Examples


#library(rgl)
yokoe3d()
#lines3d(seq(-10000,80000,900),seq(-10000,180000,900),0,col="gray")
f123()




```

**Executed Example:**
```{r yokoe3d_example, eval=TRUE, error=TRUE}
try(example('yokoe3d', package = 'yokoe', echo=TRUE, ask=FALSE), silent = TRUE)
```

